О множествах точек на плоскости с целочисленными расстояниями

### 2019-06-01 pps-linear-bound/pps-linear-lower-bound.tex
Rephrase a bit

In the present paper we improve Solymosi's results:
firstly, we obtain a greater constant $c = 5/11$ in Theorem~\ref{thm:main_estimate},
using the combined approach with the Point Packing in a Square problem
(we notice that such an approach is different from Solymosi's one);
then, we prove that $l(m,n)=1$ for all possible $m$ and $n$.

>>>>

In the present paper we improve Solymosi's results:
firstly, we obtain a greater constant $c = 5/11$ in Theorem~\ref{thm:main_estimate},
using the combined approach with the Point Packing in a Square problem
(this approach is different from Solymosi's one);
then, we prove that $l(m,n)=1$ for all possible $m$ and $n$.
